Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-09-30 edubots_surveys.Rnw
Fix error

\subsection{Survey validation}
\textcolor{blue}{

To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted. There were three items for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
Clarity was measured as an answer to the question: Is the item well presented and without ambiguity? \footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No. 
Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).

@@

% Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
Results in Figs. \ref{figure:provided*chatbots_use},
\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
show significant differences in the use of instant messaging apps between
teachers from University and vocational education. In general, most teachers
prefer messaging apps provided by their own institutions (we also show the
results for the two most popular messaging app platforms: WhatsApp and
Telegram). With respect to specific disciplines, Engineering and Technology
teachers are more active in their use, \textcolor{black}{but the number of teachers from Humanities 
who answered they used these apps in their classes is also remarkable}
(around 60\% use the apps provided by their institutions).

@@

    \caption{Use of \textcolor{black}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}

>>>>

\subsection{Survey validation}

To avoid any bias and to be sure about the quality of the questionnaire, a panel board was consulted. There were three questions for each of the items of the questionnaire which were: Clarity, Importance, Adequateness.
Clarity was measured as an answer to the question: Is the item well presented and without ambiguity? \footnote{Original text: ¿El ítem está bien redactado y sin ambigüedad?} with two choices: Yes or No. 
Both Importance and Adequateness were measured in a Likert scale from 1 to 4 (1 low, 4 high).

@@

% Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
Results in Figs. \ref{figure:provided*chatbots_use},
\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
show significant differences in the use of instant messaging apps between
teachers from University and vocational education. In general, most teachers
prefer messaging apps provided by their own institutions (we also show the
results for the two most popular messaging app platforms: WhatsApp and
Telegram). With respect to specific disciplines, Engineering and Technology
teachers are more active in their use, but the number of teachers from Humanities 
who answered they used these apps in their classes is also remarkable
(around 60\% use the apps provided by their institutions).

@@

    \caption{Use of messaging platforms either external or provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
